---
title: "Rates of On-Time Graduation at U.S. Universities"
author: "Karen Detter"
bibliography: testVisual.bib
output: 
  flexdashboard::flex_dashboard
---

```{r setup, include=FALSE}
library(flexdashboard) # always
```

## Sidebar {.sidebar}

**All graphics based on 2018 data from the U.S. Department of Education's National Center for Education Statistics. The dataset contains self-reported responses from 2,141 Institutions in the United States Granting 4-Year Degrees**


*U.S. Department of Education. (2018). National Center for Education Statistics, Integrated Postsecondary Education Data System (IPEDS), [data set]. <https://nces.ed.gov/ipeds/datacenter/InstitutionByName.aspx?goToReportId=1>*


## Column {.tabset .tabset-fade}

### Rates of 4-Year Graduation

```{r}
readRDS("ontimechart.rds")
```

### Institution Sizes (By Enrollment)

```{r}
readRDS("sizechart.rds")
```

### 4-Year Graduation Rate By Institution Size

```{r}
readRDS("bysizechart.rds")
```

### Map

```{r}

```

### References


